---
title: "descriptive_final"
author: "Moana"
date: "2025-12-12"
output: html_document
---

```{r}
library(tidyverse)
library(broom)
library(knitr)
library(kableExtra)
library(tidyr)
library(purrr)
library(lme4)
library(lmerTest)
library(mgcv)


BASE <- "/Users/moanason/Downloads/Data_ANA"

cond_cols <- c(
  "NC1" = "#87CEEB", 
  "NC2" = "#7570b3",  
  "NS"  = "#FFFFAA"  
)

info <- read_csv(file.path(BASE, "participant_info.csv")) %>%
  group_by(s_id, pair_sx) %>%
  mutate(
    dyad = factor(str_remove(s_id, "^s")),
    pair_sx = factor(pair_sx, levels = c("FF", "FM", "MM"))
  ) %>%
  dplyr::select(dyad, pair_sx)

### event_df
event_df <- read_csv(
  "/Users/moanason/Downloads/Data_ANA/descriptive_processed_event_data_with_pause.csv"
) %>%
  mutate(
    dyad      = factor(i),
    condition = recode_factor(
      as.integer(c),
      `0` = "NC1",
      `1` = "NC2",
      `2` = "NS"
    ),
    event     = as.factor(event)
  ) %>%
  left_join(info, by = "dyad")

### event_details
TrE_BET_df <- read_csv(
  "/Users/moanason/Downloads/Data_ANA/descriptive_processed_TrE_BET_IPU_data.csv"
) %>%
  mutate(
    dyad      = factor(id),
    condition = recode_factor(
      as.integer(cond),
      `0` = "NC1",
      `1` = "NC2",
      `2` = "NS"
    ),
    etype = as.factor(etype)
  ) %>%
  left_join(info, by = "dyad")

### sync_df
sr_sync <- read_csv(file.path(BASE, "turn_sync_pairs_with_F0_RMS.csv"))
sr_sync <- sr_sync %>%
  mutate(
    dyad = factor(i),
    condition = factor(
      c,
      levels = c(0, 1, 2),         
      labels = c("NC1", "NC2", "NS")
    ),
  ) %>%
  left_join(info, by = "dyad")


conv_dur <- event_df %>%
  group_by(dyad, condition) %>%
  summarise(
    conv_duration = max(time_sec + duration, na.rm = TRUE),
    .groups = "drop"
  )
```



### i 
i) Duration of each turn-constructive unit: IPU, Turn, Gaps, Backchannels, Overlaps, Silence -- what are the averaged duration of each turn-constructive unit (event) happening during the conversation per dyad, per condition? How do they (gaps and overlaps specifically) differ across different sex pairs?

```{r}

# micro-turns (IPUs) from TrE_BET_df
ipu_df <- TrE_BET_df %>%
  filter(etype == "IPU") %>%
  transmute(
    dyad, condition,
    unit     = "IPU",
    duration = duration
  )

# other events from event_df
event_units_df <- event_df %>%
  filter(event %in% c("Backchannel", "Overlap", "Pause", "Gap")) %>%
  transmute(
    dyad, condition,
    # unit     = if_else(event == "Turn", "IPU", as.character(event)),
    unit     = as.character(event),
    duration = duration,
    pair_sx = pair_sx
  )


macro_unit_df <- sr_sync %>%
  transmute(
    dyad, condition,
    unit     = "Turn", # macro_turn
    duration = D
  )

units_df <- bind_rows(ipu_df, macro_unit_df, event_units_df) %>%
  mutate(
    unit = factor(unit,
                  levels = c("Turn", "IPU", "Gap", "Pause", "Overlap", "Backchannel"))
  )

# per dyad × condition × unit: mean/median duration
dur_by_dyad <- units_df %>%
  group_by(dyad, condition, unit, pair_sx) %>%
  summarise(
    n_events   = n(),
    mean_dur   = mean(duration, na.rm = TRUE),
    median_dur = median(duration, na.rm = TRUE),
    sd_dur     = sd(duration, na.rm = TRUE),
    .groups    = "drop"
  )

# overall descriptive table (mean over dyads)
dur_overall <- dur_by_dyad %>%
  group_by(condition, unit) %>%
  summarise(
    n_dyads      = n(),
    mean_of_means = mean(mean_dur, na.rm = TRUE),
    sd_of_means   = sd(mean_dur, na.rm = TRUE),
    .groups       = "drop"
  )

# Pretty table
dur_overall %>%
  arrange(unit, condition) %>%
  kable(digits = 3,
        caption = "Mean duration (s) of turn-constructive units by condition") %>%
  kable_styling(full_width = FALSE)

```


```{r}
gap_mm <- dur_by_dyad %>%
  filter(unit == "Gap", condition %in% c("NC1", "NC2"))
ovl_mm <- dur_by_dyad %>%
  filter(unit == "Overlap", condition %in% c("NC1", "NC2"))
pause_mm <- dur_by_dyad %>%
  filter(unit == "Pause", condition %in% c("NC1", "NC2"))
m_gap <- lmer(
  mean_dur ~ condition * pair_sx + (1 | dyad),
  data = gap_mm
)
m_ovl <-lmer(
  mean_dur ~ condition * pair_sx + (1 | dyad),
  data = ovl_mm
)
m_pause <- lmer(
  mean_dur ~ condition * pair_sx + (1 | dyad),
  data = pause_mm
)
summary(m_gap)
summary(m_ovl)
summary(m_pause)
```

```{r}
mean_sum <- pause_mm %>%
  mutate(pair_sx = as.factor(pair_sx)) %>%
  group_by(pair_sx) %>%
  summarise(
    avg_dur = mean(mean_dur, na.rm = TRUE), # na.rm is safer
    .groups = "drop"
  )

mean_sum
```





```{r}
ipu_mm <- dur_by_dyad %>%
  filter(unit == "Turn", condition %in% c("NC1", "NC2"))
m_ipu <- lmer(
  mean_dur ~ condition + (1 | dyad),
  data = ipu_mm
)
summary(m_ipu)
```


```{r}
# Source - https://stackoverflow.com/a
# Posted by jan-glx, modified by community. See post 'Timeline' for change history
# Retrieved 2025-12-12, License - CC BY-SA 4.0

GeomSplitViolin <- ggproto("GeomSplitViolin", GeomViolin, 
                           draw_group = function(self, data, ..., draw_quantiles = NULL) {
  data <- transform(data, xminv = x - violinwidth * (x - xmin), xmaxv = x + violinwidth * (xmax - x))
  grp <- data[1, "group"]
  newdata <- plyr::arrange(transform(data, x = if (grp %% 2 == 1) xminv else xmaxv), if (grp %% 2 == 1) y else -y)
  newdata <- rbind(newdata[1, ], newdata, newdata[nrow(newdata), ], newdata[1, ])
  newdata[c(1, nrow(newdata) - 1, nrow(newdata)), "x"] <- round(newdata[1, "x"])

  if (length(draw_quantiles) > 0 & !scales::zero_range(range(data$y))) {
    stopifnot(all(draw_quantiles >= 0), all(draw_quantiles <=
      1))
    quantiles <- ggplot2:::create_quantile_segment_frame(data, draw_quantiles)
    aesthetics <- data[rep(1, nrow(quantiles)), setdiff(names(data), c("x", "y")), drop = FALSE]
    aesthetics$alpha <- rep(1, nrow(quantiles))
    both <- cbind(quantiles, aesthetics)
    quantile_grob <- GeomPath$draw_panel(both, ...)
    ggplot2:::ggname("geom_split_violin", grid::grobTree(GeomPolygon$draw_panel(newdata, ...), quantile_grob))
  }
  else {
    ggplot2:::ggname("geom_split_violin", GeomPolygon$draw_panel(newdata, ...))
  }
})

geom_split_violin <- function(mapping = NULL, data = NULL, stat = "ydensity", position = "identity", ..., 
                              draw_quantiles = NULL, trim = TRUE, scale = "area", na.rm = FALSE, 
                              show.legend = NA, inherit.aes = TRUE) {
  layer(data = data, mapping = mapping, stat = stat, geom = GeomSplitViolin, 
        position = position, show.legend = show.legend, inherit.aes = inherit.aes, 
        params = list(trim = trim, scale = scale, draw_quantiles = draw_quantiles, na.rm = na.rm, ...))
}
```


```{r fig.width=8, fig.height=5}
dur_plot_facet <- dur_by_dyad %>%
  filter(condition %in% c("NC1", "NC2")) %>%
  mutate(dummy = "tray")  # single x-position per facet

ggplot(
  dur_plot_facet,
  aes(x = dummy, y = mean_dur, fill = condition)
) +
  geom_split_violin(
    trim          = FALSE,
    alpha         = 0.7,
    # colour        = "black",
    draw_quantiles = c(0.25, 0.75)
  ) +
  facet_wrap(~ unit, scales = "free_y") +
  scale_fill_manual(values = cond_cols[c("NC1", "NC2")]) +
  labs(
    x = NULL,
    y = "Mean Duration per Conversation (s)",
    fill = "Condition",
    title = "Mean Duration of IPUs, Turns and Transitional Events"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x  = element_blank(),
    axis.ticks.x = element_blank(),
    strip.text   = element_text(size = 12, face = "bold"),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank()
  )
ggsave("mean_dur_events.png", path = "/Users/moanason/Downloads/Data_ANA/Fig")
```


### ii
ii) Average sum of IPU and the Turns per dyad per condition -- how many turns are averagely produced in a conversation lasting for 10 minutes? How do they differ between conditions and across different sex pairs?

```{r}
require(dplyr)

# IPU counts
ipu_counts <- TrE_BET_df %>%
  filter(etype == "IPU") %>%
  mutate(unit = "IPU") %>%
  group_by(dyad, condition, unit, pair_sx) %>%
  summarise(n_ipu = n(), .groups = "drop")

# macro-turn counts
turn_counts <- sr_sync %>%
  mutate(unit = "Turn") %>%
  group_by(dyad, condition, unit) %>%
  summarise(n_turn = n(), .groups = "drop")

# merge with conversation duration and compute per-minute rates
turns_ipu_summary <- conv_dur %>%
  left_join(ipu_counts,  by = c("dyad", "condition")) %>%
  left_join(turn_counts, by = c("dyad", "condition")) %>%
  mutate(
    n_ipu  = replace_na(n_ipu, 0L),
    n_turn = replace_na(n_turn, 0L),
    minutes = conv_duration / 60,
    ipu_per_min  = n_ipu  / minutes,
    turn_per_min = n_turn / minutes
  )

# descriptive table
turns_ipu_summary %>%
  group_by(condition) %>%
  summarise(
    mean_ipu_per_min  = mean(ipu_per_min,  na.rm = TRUE),
    sd_ipu_per_min    = sd(ipu_per_min,    na.rm = TRUE),
    mean_turn_per_min = mean(turn_per_min, na.rm = TRUE),
    sd_turn_per_min   = sd(turn_per_min,   na.rm = TRUE),
    .groups = "drop"
  ) %>%
  kable(digits = 2,
        caption = "Mean number of IPUs and macro-turns per minute") %>%
  kable_styling(full_width = FALSE)

turns_ipu_long <- turns_ipu_summary %>%
  dplyr::select(dyad, condition, ipu_per_min, turn_per_min) %>%
  pivot_longer(cols = c(ipu_per_min, turn_per_min),
               names_to = "unit", values_to = "rate_per_min") %>%
  dplyr::mutate(
    unit = recode(unit,
                  "ipu_per_min"  = "IPU",
                  "turn_per_min" = "Turn")
  )

# tests
ipu_test <- lmer(
  ipu_per_min ~ condition * pair_sx +
    (1 | dyad),
  turns_ipu_summary
)

turn_test <- lmer(
  turn_per_min ~ condition * pair_sx +
    (1 | dyad),
  turns_ipu_summary
)

summary(ipu_test)
summary(turn_test)


```

```{r fig.width=5, fig.height=3}
# turns_plot_facet <- turns_ipu_long %>%
#   filter(condition %in% c("NC1", "NC2")) %>%
#   mutate(dummy = "tray")

ggplot( 
  turns_ipu_long %>% filter(condition %in% c("NC1", "NC2")),
  aes(x = unit, y = rate_per_min, fill = condition)
) +
  geom_split_violin(
    trim          = FALSE,
    alpha         = 0.7,
    # colour        = "black",
    draw_quantiles = c(0.25, 0.75)
  ) +
  facet_wrap(~ unit, scales = "free_x") +
  scale_fill_manual(values = cond_cols) +
  labs(
    x = NULL,
    y = "Count per minute",
    fill = "Condition",
    title = "Number of IPUs and Turns per minute"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x  = element_blank(),
    axis.ticks.x = element_blank(),
    strip.text   = element_text(size = 12, face = "bold"),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank()
  )
ggsave("count_ipu_turn.png", path = "/Users/moanason/Downloads/Data_ANA/Fig")
```


### iii
iii) Proportion: N(overlaps|gaps) / N(Transitional Events) -- how are the gaps and overlaps distributed in conversations during floor transfer? How do they differ between conditions and across different sex pairs?

```{r}

# Transitional events (exclude IPUs)
trans_df <- TrE_BET_df %>%
  filter(etype != "IPU", etype != "BET", etype != "Silence", etype != "Backchannel") %>%
  mutate(
    is_overlap = etype == "Overlap",
    is_gap     = etype %in% c("Gap")
  )

trans_summary <- trans_df %>%
  group_by(dyad, condition, pair_sx) %>%
  summarise(
    n_trans   = n(),
    n_overlap = sum(is_overlap, na.rm = TRUE),
    n_gap     = sum(is_gap,     na.rm = TRUE),
    prop_overlap = n_overlap / n_trans,
    prop_gap     = n_gap     / n_trans,
    .groups      = "drop"
  )

trans_summary %>%
  group_by(condition) %>%
  summarise(
    mean_prop_overlap = mean(prop_overlap, na.rm = TRUE),
    sd_prop_overlap   = sd(prop_overlap,   na.rm = TRUE),
    mean_prop_gap     = mean(prop_gap,     na.rm = TRUE),
    sd_prop_gap       = sd(prop_gap,       na.rm = TRUE),
    .groups = "drop"
  ) %>%
  kable(digits = 3,
        caption = "Proportions of overlaps and gaps among transitional events") %>%
  kable_styling(full_width = FALSE)

# Plot: overlap and gap proportions
trans_long <- trans_summary %>%
  dplyr::select(dyad, condition, prop_overlap, prop_gap) %>%
  pivot_longer(cols = c(prop_overlap, prop_gap),
               names_to = "type", values_to = "prop") %>%
  dplyr::mutate(
    type = recode(type,
                  "prop_overlap" = "Overlap",
                  "prop_gap"     = "Gap")
  )
```

```{r  fig.height=4, fig.width=6}
ggplot(
  trans_long %>% filter(condition %in% c("NC1", "NC2")),
  aes(x = type, y = prop, fill = condition)
) +
  geom_boxplot(
    position = position_dodge(width = 0.9),
    alpha = 1.0
  ) +
  geom_jitter(
    aes(),
    position = position_jitterdodge(
      jitter.width = 0.12,
      dodge.width  = 0.75
    ),
    alpha = 0.5,
    size = 1.5
  ) +
  scale_color_manual(values = cond_cols) +
  scale_fill_manual(values = cond_cols) +
  labs(
    x = "Transitional Event Type",
    y = "Proportion of Transitional Events",
    fill = "Condition",
    color = "Condition",
    title = "Distribution of Gaps and Overlaps during Floor Transfer"
  ) +
  theme_minimal() +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank()
  )
ggsave("distribution_tre.png", path = "/Users/moanason/Downloads/Data_ANA/Fig")
```


```{r}
trans_test_ovlp <- lmer(
  prop_overlap ~ condition * pair_sx +
    (1 | dyad), 
  trans_summary
)
trans_test_gap <- lmer(
  prop_gap ~ condition * pair_sx +
    (1 | dyad), 
  trans_summary
)
summary(trans_test_ovlp)
summary(trans_test_gap)
```


### iv)
iv) Density: N(Backchannels) / Time -- how often are the backchannels produced in a 10-min conversation? 

```{r}

bc_counts <- event_df %>%
  filter(event == "Backchannel") %>%
  group_by(dyad, condition, pair_sx) %>%
  summarise(
    n_bc   = n(),
    dur_bc = sum(duration, na.rm = TRUE),
    .groups = "drop"
  )

bc_summary <- conv_dur %>%
  left_join(bc_counts, by = c("dyad", "condition")) %>%
  mutate(
    n_bc   = replace_na(n_bc,   0L),
    dur_bc = replace_na(dur_bc, 0),
    minutes       = conv_duration / 60,
    bc_per_min    = n_bc / minutes,
    bc_time_ratio = dur_bc / conv_duration
  )

bc_summary %>%
  group_by(condition) %>%
  summarise(
    mean_bc_per_min    = mean(bc_per_min,    na.rm = TRUE),
    sd_bc_per_min      = sd(bc_per_min,      na.rm = TRUE),
    mean_bc_time_ratio = mean(bc_time_ratio, na.rm = TRUE),
    sd_bc_time_ratio   = sd(bc_time_ratio,   na.rm = TRUE),
    .groups = "drop"
  ) %>%
  kable(digits = 3,
        caption = "Backchannel density and time proportion by condition") %>%
  kable_styling(full_width = FALSE)
```



```{r fig.height=4, fig.width=6}
ggplot(
  bc_summary %>%
  aes(x = condition, y = bc_per_min, fill = condition)
) +
  geom_boxplot(width = 0.5, colour = "black") +
  geom_jitter(width = 0.2, alpha = 0.5) +
  scale_fill_manual(values = cond_cols[c("NC1", "NC2")]) +
  # facet_grid(~ pair_sx) +
  labs(
    x = "Condition",
    y = "Backchannels per minute",
    fill = "Condition",
    title = "Frequency of Backchannels in 10-min Conversation"
  ) +
  theme_minimal()+
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank()
  )
ggsave("bc_frequency.png", path = "/Users/moanason/Downloads/Data_ANA/Fig")
```
```{r}
bc_sx_tests <- lmer(
  bc_time_ratio ~ condition + pair_sx + 
    (1 | dyad),
  bc_summary
)
summary(bc_sx_tests)
```

--------------------------------------------------------------------------------
# summary of all descriptive results

```{r}
library(dplyr)
library(tidyr)
library(kableExtra)

tab_duration <- dur_overall %>%
  filter(condition %in% c("NC1", "NC2")) %>%
  transmute(
    category  = "Duration",
    measure   = "Mean duration (s)",
    unit      = as.character(unit),
    condition = condition,
    mean      = mean_of_means,
    sd        = sd_of_means
  )

tab_turns <- turns_ipu_long %>%
  filter(condition %in% c("NC1", "NC2")) %>%
  group_by(condition, unit) %>%
  summarise(
    n_dyads = n_distinct(dyad),
    mean    = mean(rate_per_min, na.rm = TRUE),
    sd      = sd(rate_per_min,   na.rm = TRUE),
    .groups = "drop"
  ) %>%
  transmute(
    category  = "Turn frequency",
    measure   = "Count per minute",
    unit      = unit,
    condition = condition,
    mean, sd
  )

tab_trans <- trans_long %>%
  filter(condition %in% c("NC1", "NC2")) %>%
  group_by(condition, type) %>%
  summarise(
    n_dyads = n_distinct(dyad),
    mean    = mean(prop, na.rm = TRUE),
    sd      = sd(prop,   na.rm = TRUE),
    .groups = "drop"
  ) %>%
  transmute(
    category  = "Transitional distribution",
    measure   = "Proportion of transitional events",
    unit      = type,        # "Gap" / "Overlap"
    condition = condition,
    mean, sd
  )

tab_bc_per_min <- bc_summary %>%
  filter(condition %in% c("NC1", "NC2")) %>%
  group_by(condition) %>%
  summarise(
    n_dyads = n_distinct(dyad),
    mean    = mean(bc_per_min,    na.rm = TRUE),
    sd      = sd(bc_per_min,      na.rm = TRUE),
    .groups = "drop"
  ) %>%
  transmute(
    category  = "Backchannel density",
    measure   = "Backchannels per minute",
    unit      = "Backchannel",
    condition = condition,
    mean, sd
  )

tab_bc_time_ratio <- bc_summary %>%
  filter(condition %in% c("NC1", "NC2")) %>%
  group_by(condition) %>%
  summarise(
    n_dyads = n_distinct(dyad),
    mean    = mean(bc_time_ratio, na.rm = TRUE),
    sd      = sd(bc_time_ratio,   na.rm = TRUE),
    .groups = "drop"
  ) %>%
  transmute(
    category  = "Backchannel density",
    measure   = "Proportion of time spent in BC",
    unit      = "Backchannel",
    condition = condition,
    mean, sd
  )

tab_bc <- bind_rows(tab_bc_per_min, tab_bc_time_ratio)

summary_all <- bind_rows(
  tab_duration,
  tab_turns,
  tab_trans,
  tab_bc
) %>%
  arrange(category, unit, condition)

summary_all %>%
  kable(digits = 3,
        col.names = c("Category", "Measure", "Unit",
                      "Condition", "Mean", "SD"),
        caption = "Descriptive statistics of turn-taking and backchannel behaviour") %>%
  kable_styling(full_width = FALSE)

```

```{r}
write.csv(
  summary_all,
  "/Users/moanason/Downloads/Data_ANA/descriptive_summary_table.csv",
  row.names = FALSE
)
```

```{r}
require(gt)
gt_summary <- summary_all %>%
  mutate(
    Mean = round(mean, 3),
    SD   = round(sd,   3)
  ) %>%
  dplyr::select(Category = category,
         Measure  = measure,
         Unit     = unit,
         Condition = condition,
         Mean, SD) %>%
  gt(groupname_col = "Category") %>%
  tab_header(
    title = "Descriptive statistics of turn-taking and backchannel behaviour"
  ) %>%
  fmt_number(columns = c(Mean, SD), decimals = 3) %>%
  cols_align(align = "left", columns = c(Measure, Unit)) %>%
  cols_align(align = "center", columns = c(Condition)) %>%
  cols_align(align = "right", columns = c(Mean, SD)) %>%
  tab_options(
    table.width = pct(100),
    row_group.as_column = FALSE
  )

gt_summary
# gtsave(gt_summary, "summary_all_gt.png", path = "/Users/moanason/Downloads/Data_ANA/Tab")
```


```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(kableExtra)

names(summary_all)
##    z = (Mean - grand_mean_of_Mean) / sd_of_Mean
##    for each Category × Measure across all Unit × Condition

summary_z <- summary_all %>%
  mutate(
    var_label = paste(category, measure, sep = " – ")
  ) %>%
  group_by(var_label) %>%
  mutate(
    z_mean = (mean - mean(mean, na.rm = TRUE)) /
             sd(mean,  na.rm = TRUE)
  ) %>%
  ungroup()

summary_z %>%
  arrange(category, measure, unit, condition) %>%
  kable(
    digits = 3,
    caption = "Standardised (z) descriptive measures across event types"
  ) %>%
  kable_styling(full_width = FALSE)



summary_z <- summary_z %>%
  mutate(
    condition = factor(condition, levels = c("NC1", "NC2"))
  )

unit_levels <- c("Turn", "IPU", "Gap", "Pause", "Overlap", "Backchannel")
summary_z <- summary_z %>%
  mutate(
    unit = factor(unit, levels = unit_levels)
  )

summary_z <- summary_z %>%
  mutate(
    var_label = dplyr::recode(
      var_label,
      "Duration – Mean duration (s)"                 = "Duration",
      "Turn frequency – Count per minute"            = "Turn count / min",
      "Transitional distribution – Proportion of transitional events" = "Gaps / Overlaps",
      "Backchannel density – Backchannels per minute" = "BC / minute",
      "Backchannel density – Proportion of time spent in BC" = "BC time ratio",
      .default = var_label
    )
  )
```

```{r figure z-scores, fig.height=3, fig.width=10, cache=FALSE}
ggplot(
  summary_z %>% 
    filter(condition %in% c("NC1", "NC2")) %>%
    filter(!var_label %in% c("BC / minute", "BC time ratio")),
  aes(x = unit, y = z_mean, fill = condition)
) +
  # zero line
  geom_hline(yintercept = 0, colour = "grey30", size = 0.4) +
  geom_hline(yintercept =  1, linetype = "dashed", colour = "grey70", size = 0.3) +
  geom_hline(yintercept = -1, linetype = "dashed", colour = "grey70", size = 0.3) +
  
  # grouped bars per Unit, per Condition
  geom_col(
    position = position_dodge(width = 1.0),
    width    = 0.6,
    colour   = "black"
  ) +
  
  facet_grid(
    ~ var_label,
    scales = "free_x",
    space  = "free_x"
  ) +
  
  scale_fill_manual(values = cond_cols[c("NC1", "NC2")]) +
  
  labs(
    x = NULL,
    y = "z-score (within measure)",
    fill = "Condition",
    title = "Standardised Distribution of Turn-taking Indices"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x  = element_text(angle = 30, hjust = 1, size = 9),
    strip.text   = element_text(size = 11, face = "bold"),
    panel.spacing = unit(0.8, "lines"),
    legend.position = "top"
  )
ggsave("distribution_zscore_all.png", path = "/Users/moanason/Downloads/Data_ANA/Fig")
```
