---
title: "prediction_analysis_markov_turntaking"
author: "Moana"
date: "2025-11-22"
output:
  pdf_document: default
  html_document: default
---

```{r}
library(tidyverse)
library(lme4)
library(lmerTest)

DATA_ROOT <- "/Users/moanason/Downloads/Data_ANA"


cond_cols <- c(
  "NC1" = "#87CEEB", 
  "NC2" = "#7570b3",  
  "NS"  = "#FFFFAA"  
)


# ---- Frame-wise data (20 ms frames) ----
frame_df <- read_csv(file.path(DATA_ROOT, "temporal_processed_data_frames.csv")) %>%
  mutate(
    dyad = factor(id),
    condition = factor(
      cond,
      levels = c(0, 1, 2),
      labels = c("NC1", "NC2", "NS")
    )
  )

# Expect columns something like:
# id, cond, time_sec, spk1, spk2, F0_A, RMS_A, F0_B, RMS_B, ...

# ---- TrE/BET/IPU data ----
# IPU = Inter-pausel units (the second-last level of segment of continuous speech from one speaker)
# BET = Between event turns (the minimal segmentation level where IPUs (one Turn component) were broke by events, mostly backchannels from the other speaker)
# Silence = also the minimal segmentation level where the Pauses (the other Turn component) were broke by events, mostly backchannels from the other speaker. 
# Thus: IPU = BET (not necessarily exist)  + BET overlapped with a Backchannel from the other speaker, which doesn't count for the current IPU from the current speaker + BET (not necessarily exist); Pause = Silence (not necessarily exist) + Silence overlapped with a Backchannel from the other speaker, which doesn't count for the current IPU from the current speaker + Silence (not necessarily exist) 
tre_df <- read_csv(file.path(DATA_ROOT, "descriptive_processed_TrE_BET_IPU_data.csv")) %>%
  mutate(
    dyad = factor(id),
    condition = factor(
      cond,
      levels = c(0, 1, 2),
      labels = c("NC1", "NC2", "NS")
    )
  )

# Expect columns:
# id, cond, etype, event, label, spk, spk1, spk2,
# n_syl_A, n_syl_B, sr_A, sr_B, sr,
# F0_A, RMS_A, F0_B, RMS_B, duration, time_sec

```

### Markov chain over joint speech activity (S_0, S_A, S_B, S_AB)
```{r}
# define joint state
# Joint state based on spk1 / spk2:
#   S_0  = no one speaking
#   S_A  = only A speaking
#   S_B  = only B speaking
#   S_AB = both speaking (overlap)

joint_states <- frame_df %>%
  mutate(
    state = case_when(
      spk1 == 0 & spk2 == 0 ~ "S_0",
      spk1 == 1 & spk2 == 0 ~ "S_A",
      spk1 == 0 & spk2 == 1 ~ "S_B",
      spk1 == 1 & spk2 == 1 ~ "S_AB",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(state)) %>%
  arrange(dyad, condition, time_sec)

```


```{r}
# build transitions and transition probabilities per dyad × condition

joint_transitions <- joint_states %>%
  group_by(dyad, condition) %>%
  arrange(time_sec, .by_group = TRUE) %>%
  mutate(
    state_next = lead(state)
  ) %>%
  filter(!is.na(state_next)) %>%
  group_by(dyad, condition, state) %>%
  dplyr::count(state_next, name = "n") %>%
  group_by(dyad, condition, state) %>%
  mutate(
    p = n / sum(n)  # row-wise normalisation
  ) %>%
  ungroup()

joint_transitions %>% head()
# joint_transitions is a long-format Markov matrix: for each (dyad,condition,state) you have p(state_next | state).

```

```{r}
joint_transitions %>%
  dplyr::filter(dyad == "10", condition == "NC1") %>%
  dplyr::select(state, state_next, p) %>%
  pivot_wider(names_from = state_next, values_from = p)
# the full 4×4 matrix for a specific dyad
```


#### derived “turn-taking style” measures per dyad × condition
```{r}
joint_style <- joint_transitions %>%
  group_by(dyad, condition) %>%
  summarise(
    p_switch = sum(p[state == "S_A" & state_next == "S_B"]) +
               sum(p[state == "S_B" & state_next == "S_A"]),
    p_overlap_onset = sum(p[state == "S_A" & state_next == "S_AB"]) +
                      sum(p[state == "S_B" & state_next == "S_AB"]),
    p_gap_after_speech = sum(p[state == "S_A" & state_next == "S_0"]) +
                         sum(p[state == "S_B" & state_next == "S_0"]),
    p_stay_speaking = (
      sum(p[state == "S_A" & state_next == "S_A"]) +
      sum(p[state == "S_B" & state_next == "S_B"])
    ) / 2,
    .groups = "drop"
  )

joint_style

```


```{r}
joint_style_nc <- joint_style %>%
  filter(condition %in% c("NC1", "NC2"))

m_switch <- lmer( # probability of smooth floor switch after speech
  p_switch ~ condition + (1 | dyad),
  data = joint_style_nc
)
summary(m_switch)
anova(m_switch)

m_stay <- lmer( # probability of smooth floor switch after speech
  p_stay_speaking ~ condition + (1 | dyad),
  data = joint_style_nc
)
summary(m_stay)
anova(m_stay)

m_overlap <- lmer( # probability of overlap after one's speech
  p_overlap_onset ~ condition + (1 | dyad),
  data = joint_style_nc
)
summary(m_overlap)
anova(m_overlap)

m_gap <- lmer( # probability of going to silence after one's speech
  p_gap_after_speech ~ condition + (1 | dyad),
  data = joint_style_nc
)
summary(m_gap)
anova(m_gap)
```


```{r fig.height=5, fig.width=6}
joint_style_nc %>%
  pivot_longer(cols = c(p_switch, p_overlap_onset, p_gap_after_speech, p_stay_speaking),
               names_to = "measure", values_to = "value") %>%
  mutate(
    measure = recode(
      measure,
      p_switch   = "P(Speaker Switch)",
      p_overlap_onset   = "P(Overlap | IPU)",
      p_gap_after_speech  = "P(Gap | IPU)",
      p_stay_speaking = "P(Speaker Stay (IPUs))"
    )
  ) %>%
  ggplot(aes(x = condition, y = value, fill = condition)) +
  geom_boxplot(outlier.alpha = 0.7) +
  geom_point(alpha = 0.3, col = "black") +
  facet_wrap(~ measure, scales = "free_y") +
  scale_color_manual(values = cond_cols) +
  scale_fill_manual(values = cond_cols) +
  labs(
    x = "Condition",
    y = "Probability",
    fill = "Condition",
    title = "Turn-taking measures (joint speech states)"
  ) +
  theme_minimal() +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank()
  )
ggsave("joint_speech_states.png", path = "/Users/moanason/Downloads/Data_ANA/Fig")

```



### Markov chain over event labels (T_A, T_B, BC_A, BC_B, GAP, SIL, OVL)
```{r}
event_seq <- tre_df %>%
  mutate(
    state = case_when(
      etype == "BET"         & spk == 0 ~ "T_A",
      etype == "BET"         & spk == 1 ~ "T_B",
      etype == "Backchannel" & spk == 0 ~ "BC_A",
      etype == "Backchannel" & spk == 1 ~ "BC_B",
      etype == "Gap"                     ~ "GAP",
      etype == "Silence"                 ~ "SIL",
      etype == "Overlap"                 ~ "OVL",
      TRUE                               ~ NA_character_
    )
  ) %>%
  filter(!is.na(state)) %>%
  arrange(dyad, condition, time_sec)

event_seq %>% head()

# event-level Markov transitions per dyad × condition
event_transitions <- event_seq %>%
  group_by(dyad, condition) %>%
  arrange(time_sec, .by_group = TRUE) %>%
  mutate(
    state_next = lead(state)
  ) %>%
  filter(!is.na(state_next)) %>%
  group_by(dyad, condition, state) %>%
  dplyr::count(state_next, name = "n") %>%
  group_by(dyad, condition, state) %>%
  mutate(
    p = n / sum(n)
  ) %>%
  ungroup()

event_transitions %>% head()


# for a specific dyad-condition we can see the full transition matrix
event_transitions %>%
  dplyr::filter(dyad == "10", condition == "NC1") %>%
  dplyr::select(state, state_next, p) %>%
  pivot_wider(names_from = state_next, values_from = p)


```

#### derived measures about backchannels and turn patterns
p_BC_given_speech: probability that a turn from one speaker is followed by a backchannel from the other. {P(TA​→BCB​)+P(TB​→BCA​)}

p_switch_after_BC: probability that a backchannel is followed by a floor switch (listener takes the turn) {P(BCB​→TB​)+P(BCA​→TA​)}

p_ovl_after_speech: probability that a turn is followed by an overlap {P(TA​→OVL)+P(TB​→OVL)}

```{r}
event_style <- event_transitions %>%
  group_by(dyad, condition) %>%
  summarise(
    p_BC_given_speech = sum(p[state == "T_A" & state_next == "BC_B"]) +
                   sum(p[state == "T_B" & state_next == "BC_A"]),
    p_switch_after_BC = sum(p[state == "BC_B" & state_next == "T_B"]) +
                        sum(p[state == "BC_A" & state_next == "T_A"]),
    p_ovl_after_speech = sum(p[state == "T_A" & state_next == "OVL"]) +
                    sum(p[state == "T_B" & state_next == "OVL"]),
    .groups = "drop"
  )

event_style

```


```{r}
event_style_nc <- event_style %>%
  filter(condition %in% c("NC1", "NC2"))


m_BC_given_T <- lmer(
  p_BC_given_speech ~ condition + (1 | dyad),
  data = event_style_nc
)
summary(m_BC_given_T)
anova(m_BC_given_T)

m_switch_after_BC <- lmer(
  p_switch_after_BC ~ condition + (1 | dyad),
  data = event_style_nc
)
summary(m_switch_after_BC)
anova(m_switch_after_BC)

m_ovl_after_T <- lmer(
  p_ovl_after_speech ~ condition + (1 | dyad),
  data = event_style_nc
)
summary(m_ovl_after_T)
anova(m_ovl_after_T)

```


```{r fig.width=8, fig.height=4}
event_style_nc %>%
  pivot_longer(cols = c(p_BC_given_speech, p_switch_after_BC, p_ovl_after_speech),
               names_to = "measure", values_to = "value") %>%
  mutate(
    measure = recode(
      measure,
      p_BC_given_speech   = "P(BC | IPU)",
      p_switch_after_BC   = "P(Switch | BC)",
      p_ovl_after_speech  = "P(Overlap | IPU)"
    )
  ) %>%
  ggplot(aes(x = condition, y = value, fill = condition)) +
  geom_boxplot(outlier.alpha = 0.7) +
  geom_point(alpha = 0.3) +
  facet_wrap(~ measure, scales = "free_y") +
  scale_color_manual(values = cond_cols) +
  scale_fill_manual(values = cond_cols) +
  labs(
    x = "Condition",
    y = "Probability",
    fill = "Condition",
    title = "Conditional Patterns for Overlapping Events (Speech / Backchannels / Overlaps)"
  ) +
  theme_minimal() +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank()
  )
ggsave("conditional_patterns_for_events.png", path = "/Users/moanason/Downloads/Data_ANA/Fig")
```














