---
title: "synchronicity_analysis_turns"
author: "Moana"
date: "2025-11-20"
output:
  pdf_document: default
  html_document: default
---

```{r}
library(tidyverse)
library(lme4)
library(lmerTest)
library(mgcv)
library(broom)
library(knitr)
library(kableExtra)
library(tidyr)
library(purrr)
library(mgcv)


cond_cols <- c(
  "NC1" = "#87CEEB", 
  "NC2" = "#7570b3",  
  "NS"  = "#FFFFAA"  
)

DATA_ROOT <- "/Users/moanason/Downloads/Data_ANA"

info <- read_csv(file.path(DATA_ROOT, "participant_info.csv")) %>%
  mutate(
    dyad = as.factor(str_remove(s_id, "^s")),
    pair_sx = factor(pair_sx, levels = c("FF", "FM", "MM"))
  ) %>%
  dplyr::select(dyad, pair_sx)

sr_sync <- read_csv(file.path(DATA_ROOT, "turn_sync_pairs_with_F0_RMS.csv"))

# Recode dyad and condition
sr_sync <- sr_sync %>%
  mutate(
    dyad = factor(i),
    condition = factor(
      c,
      levels = c(0, 1, 2),         
      labels = c("NC1", "NC2", "NS")
    ),
    # logM = log(M_rate + 1e-6)  # avoid log(0), apply only when the value is huge
  ) %>%
  left_join(info, by = "dyad")

frame_df <- read_csv(file.path(DATA_ROOT, "temporal_processed_data_frames.csv"))

frame_df <- frame_df %>%
  mutate(
    dyad = factor(id),
    condition = factor(
      cond,
      levels = c(0, 1, 2),
      labels = c("NC1", "NC2", "NS")
    ),
    # only keep F0/RMS when speaker is active
    F0_A_sp  = if_else(spk1 == 1, F0_A,  NA_real_),
    F0_B_sp  = if_else(spk2 == 1, F0_B,  NA_real_),
    RMS_A_sp = if_else(spk1 == 1, RMS_A, NA_real_),
    RMS_B_sp = if_else(spk2 == 1, RMS_B, NA_real_)
  ) %>%
  left_join(info, by = "dyad")

sr_sync %>% head()
```

# i) global convergence analysis
## first, global similarity & convergence over the three features
### mean mismatch per dyad & condition for speech rate
```{r}
sr_sync_summary <- sr_sync %>%
  group_by(dyad, condition) %>%
  summarise(
    n_pairs  = n(),
    mean_M   = mean(M_rate, na.rm = TRUE),
    median_M = median(M_rate, na.rm = TRUE),
    mean_Delta   = mean(Delta_rate, na.rm = TRUE),
    median_Delta = median(Delta_rate, na.rm = TRUE),
    .groups = "drop"
  )

sr_sync_summary

```


```{r}
ggplot(sr_sync_summary, aes(x = condition, y = mean_M, colour = condition)) +
  geom_boxplot() +
  scale_color_manual(values = cond_cols) +
  scale_fill_manual(values = cond_cols) +
  labs(
    y = "Mean speech-rate mismatch |Delta| (syll/s)",
    x = "Condition"
  )
```
### mixed model for speech rate (M_rate = speech rate deviation each turn-pair)
```{r}
sr_nc <- sr_sync %>%
  filter(condition %in% c("NC1", "NC2"))

m_sr_mean <- lmer(
  Delta_rate ~ condition + (1 | dyad),
  data = sr_nc
)

summary(m_sr_mean)
anova(m_sr_mean)

```


### global prosodic features analysis 
```{r}
sync_df <- read_csv(file.path(DATA_ROOT, "turn_sync_pairs_with_F0_RMS.csv"))

sync_df <- sync_df %>%
  mutate(
    dyad = factor(i),
    condition = factor(
      c,
      levels = c(0, 1, 2),
      labels = c("NC1", "NC2", "NS")
    ),
    # avoid log(0)
    logF0dev  = log(F0_dev  + 1e-6), # optional
    logRMSdev = log(RMS_dev + 1e-6),
    logMrate  = log(M_rate  + 1e-6)
  ) %>%
  left_join(info, by = "dyad")
  # With logM, big mismatches are compressed; this can reduce apparent differences if our main condition effect sits in the “large-mismatch” tail,
  # but we can stick with M_rate, F0_dev and RMS_dev, large values have full weight.


# if only nc
sync_nc <- sync_df %>%
  filter(condition %in% c("NC1", "NC2"))

```

### global f0 deviation 
```{r global F0 deviation} 
m_f0 <- lmer( # higher deviation, less synchrony
  F0_dev ~ condition + (1 | dyad),
  data = sync_nc %>% filter(!is.na(F0_dev))
)

summary(m_f0)
anova(m_f0)

```

### global RMS deviation
```{r global RMS deviation}
m_rms <- lmer( # higher deviation, less synchrony
  RMS_dev ~ condition + (1 | dyad),
  data = sync_nc %>% filter(!is.na(RMS_dev))
)

summary(m_rms)
anova(m_rms)

```


## then, global (Half-Half) similarity & convergence 

```{r}
# add half label, define the first half and the second half by the median time_sec
frame_half <- frame_df %>%
  group_by(dyad, condition) %>%
  mutate(
    half = if_else(time_sec <= median(time_sec, na.rm = TRUE), "H1", "H2")
  ) %>%
  ungroup()

# compute
global_by_half <- frame_half %>%
  group_by(dyad, condition, half) %>%
  summarise(
    F0_A_mean  = mean(F0_A_sp,  na.rm = TRUE),
    F0_B_mean  = mean(F0_B_sp,  na.rm = TRUE),
    RMS_A_mean = mean(RMS_A_sp, na.rm = TRUE),
    RMS_B_mean = mean(RMS_B_sp, na.rm = TRUE),
    .groups = "drop"
  )

global_by_half
```


```{r}
# reshape per dyad condition
global_wide <- global_by_half %>%
  pivot_wider(
    id_cols = c(dyad, condition),
    names_from = half,
    values_from = c(F0_A_mean, F0_B_mean, RMS_A_mean, RMS_B_mean)
  )

# Global similarity (absolute difference) and convergence (H1 diff - H2 diff)
global_metrics <- global_wide %>%
  mutate(
    # similarity: smaller diff = more entrained
    F0_diff_H1  = abs(F0_A_mean_H1  - F0_B_mean_H1),
    F0_diff_H2  = abs(F0_A_mean_H2  - F0_B_mean_H2),
    RMS_diff_H1 = abs(RMS_A_mean_H1 - RMS_B_mean_H1),
    RMS_diff_H2 = abs(RMS_A_mean_H2 - RMS_B_mean_H2),

    F0_convergence  = F0_diff_H1  - F0_diff_H2,
    RMS_convergence = RMS_diff_H1 - RMS_diff_H2
  )

global_metrics

```

# mixed models for global (Half-Half) similarity / convergence
```{r}
# Global similarity (take whole convo average of diff)
global_sim <- global_metrics %>%
  mutate(
    F0_diff_mean  = (F0_diff_H1  + F0_diff_H2) / 2,
    RMS_diff_mean = (RMS_diff_H1 + RMS_diff_H2) / 2
  )

m_F0_sim <- lmer(F0_diff_mean ~ condition + (1 | dyad), data = global_sim)
summary(m_F0_sim)
anova(m_F0_sim)

m_RMS_sim <- lmer(RMS_diff_mean ~ condition + (1 | dyad), data = global_sim)
summary(m_RMS_sim)
anova(m_RMS_sim)

# convergence
m_F0_conv <- lmer(F0_convergence ~ condition + (1 | dyad), data = global_metrics)
summary(m_F0_conv)
anova(m_F0_conv)

m_RMS_conv <- lmer(RMS_convergence ~ condition + (1 | dyad), data = global_metrics)
summary(m_RMS_conv)
anova(m_RMS_conv)

```





# ii) Local convergence: Time-resolved synchrony: GAM on |Delta(n)| over time

```{r}
DATA_ROOT <- "/Users/moanason/Downloads/Data_ANA"

sr_sync <- read_csv(file.path(DATA_ROOT, "turn_sync_pairs_with_F0_RMS.csv"))

sr_sync <- sr_sync %>%
  mutate(
    dyad = factor(i),
    condition = factor(
      c,
      levels = c(0, 1, 2),              # adjust if NS not present yet
      labels = c("NC1", "NC2", "NS")
    ),
    # small epsilon to avoid log(0)
    logM = log(M_rate + 1e-6)
  ) %>%
  left_join(info, by = "dyad")

sr_sync <- sr_sync %>%
  group_by(dyad, condition) %>%
  mutate(
    # ensure pair_idx is 0..K-1 within each conversation
    pair_idx = row_number() - 1,
    t_rel_idx = pair_idx / max(pair_idx)   # 0 .. 1 (relative index)
  ) %>%
  ungroup()


sync_nc <- sr_sync %>% # considering the time
  group_by(dyad, condition) %>%
  arrange(pair_idx, .by_group = TRUE) %>%
  mutate(
    pair_dur = D + D_next,                 # duration represented by this pair
    t_cum_end = cumsum(pair_dur),          # elapsed time (end of this pair)
    t_cum_mid = t_cum_end - pair_dur/2,    # elapsed time (midpoint of this pair)
    t_rel = t_cum_mid / max(t_cum_mid, na.rm = TRUE)  # 0–1 within dyadxcondition
  ) %>%
  ungroup()


sr_nc %>% head()

```

## Time-resolved speechrate synchrony, turn-by-turn (turn-pair)
```{r}
# local convergence (does that difference shrink over successive switches?): Cn​=P_n​−P_n+1​, P_n on conversation progress (t_rel_idx); a negative slope indicates convergence: deviation down, interlocutor coupling up
gam_sr_rel <- gam(
    M_rate ~ condition +
    s(t_rel, by = condition, k = 40) + 
      s(dyad, bs = "re"),
  data = sync_nc,
  method = "REML",
  weights = pair_dur, 
  family = Gamma(link = "log")
)

summary(gam_sr_rel)
plot(gam_sr_rel, pages = 1, shade = TRUE)

```

```{r from stackoverflow}
library(ggplot2)
library(dplyr)
library(mgcv)

# We generate a sequence of time points for every condition
new_data <- expand.grid(
  t_rel = seq(min(sync_nc$t_rel), max(sync_nc$t_rel), length.out = 200),
  condition = unique(sr_nc$condition),
  # We need to include 'dyad' to satisfy the model object, 
  # but we will exclude its effect in the prediction step.
  dyad = sync_nc$dyad[1] 
)

# 2. Predict Values (Excluding Random Effects)
# We use exclude = "s(dyad)" so we predict for an "average" dyad
pred <- predict(
  gam_sr_rel, 
  newdata = new_data, 
  se.fit = TRUE, 
  type = "link",         # Predictions on the link scale
  exclude = "s(dyad)"    # CRITICAL: Ignore the random effect
)

# 3. Add predictions and CI to the new_data frame
new_data <- new_data %>%
  mutate(
    fit = pred$fit,
    se = pred$se.fit,
    # Calculate 95% Confidence Intervals
    lower = fit - 1.96 * se,
    upper = fit + 1.96 * se
  )

ggplot(new_data, aes(x = t_rel, y = fit, color = condition, fill = condition)) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, color = NA) +
  geom_line(linewidth = 1) +
  # Aesthetic Customization
  # scale_color_brewer(palette = "Dark2") + # Elegant color palette
  # scale_fill_brewer(palette = "Dark2") +
  scale_color_manual(values = cond_cols) +
  scale_fill_manual(values = cond_cols) +
  labs(
    x = "Relative Time Index",
    y = "Predicted M_rate",
    title = "Modelled Rate by Condition",
    subtitle = "GAM prediction excluding random dyadic effects"
  ) +
  theme_minimal(base_size = 14) +
  theme(legend.position = "top")
```


```{r fig.width=6, fig.height=4}
# e.g. 20 bins across the conversation for dynamic change over time (turn-by-turn)
sr_bins <- sync_nc %>%
  mutate(
    bin = cut(
      t_rel,
      breaks = seq(0, 1, length.out = 21),
      include.lowest = TRUE,
      labels = FALSE
    )
  ) %>%
  mutate(
    M_rate = -M_rate,
  ) %>%
  group_by(condition, bin) %>%
  summarise(
    M_mean = mean(M_rate, na.rm = TRUE),
    M_se   = sd(M_rate, na.rm = TRUE) / sqrt(n()),
    .groups = "drop"
  ) %>%
  mutate(
    bin_center = (bin - 0.5) / 20   # 0.1, 0.3, 0.5, 0.7, 0.9
  )

ggplot(sr_bins,
       aes(x = bin_center, y = M_mean, colour = condition, group = condition)) +
  geom_line(linewidth = 0.5, alpha = 0.7) +
  geom_point(alpha = 0.7) +
  scale_color_manual(values = cond_cols) +
  scale_fill_manual(values = cond_cols) +
  # geom_smooth(stat = "smooth",
  # position = "identity", se = F, linewidth = 0.7) +
  geom_errorbar(aes(ymin = M_mean - M_se, ymax = M_mean + M_se), width = 0.01, alpha = 0.2) +
  labs(
    x = "Conversation progress (0 ~ 1)",
    y = "Mean SR mismatch -|Delta| (syl/s): -|Delta|0 = more sync",
    colour = "Condition"
  ) +
  theme_minimal() +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank()
  )
ggsave("mean_sr_dev.png", path = "/Users/moanason/Downloads/Data_ANA/Fig")

```

## Time-resolved F0 / RMS synchrony (GAM over progress), local convergence - dynamics
```{r}
gam_f0 <- gam(
  F0_rate ~ condition +
    s(t_rel, by = condition, k = 40) +
    s(dyad, bs = "re"),
  data = sync_nc %>% filter(!is.na(F0_rate)),
  method = "REML",
  weights = pair_dur,
  family = "Gamma"(link = "log")
)

summary(gam_f0)
plot(gam_f0, pages = 1, shade = TRUE)

```


```{r}
gam_rms <- gam(
  RMS_rate ~ condition +
    s(t_rel, by = condition, k = 6) +
    s(dyad, bs = "re"),
  data = sync_nc %>% filter(!is.na(RMS_rate)),
  method = "REML",
  weights = pair_dur,
  family = "Gamma"(link = "log")
)

summary(gam_rms)
plot(gam_rms, pages = 1, shade = TRUE)

```


```{r}
# 20 bins across progress
f0_bins <- sync_nc %>%
  filter(!is.na(F0_rate)) %>%
  mutate(
    bin = cut(t_rel,
              breaks = seq(0, 1, length.out = 21),
              include.lowest = TRUE,
              labels = FALSE)
  ) %>%
  group_by(condition, bin) %>%
  summarise(
    F0_mean = mean(F0_rate, na.rm = TRUE),
    F0_se   = sd(F0_rate, na.rm = TRUE) / sqrt(n()),
    .groups = "drop"
  ) %>%
  mutate(
    bin_center = (bin - 0.5) / 5
  )

ggplot(f0_bins, # visualisation for f0
       aes(x = bin_center, y = F0_mean, colour = condition, group = condition)) +
  geom_line(size = 0.5) +
  geom_point() +
  scale_color_manual(values = cond_cols) +
  scale_fill_manual(values = cond_cols) +
  geom_errorbar(aes(ymin = F0_mean - F0_se,
                    ymax = F0_mean + F0_se),
                width = 0.02) +
  labs(
    x = "Conversation progress (0 = early, 1 = late)",
    y = "Mean F0 mismatch |Delta_F0| (z units)",
    colour = "Condition"
  )

```


### plot a joint plot for gamm --- time-resolved local deviation of the three features
```{r fig.height=4, fig.width=12} 
library(ggplot2)
library(dplyr)
library(mgcv)


cond_cols <- c(
  "NC1" = "#87CEEB", 
  "NC2" = "#7570b3",  
  "NS"  = "#FFFFAA"  
)

get_gam_pred <- function(model, original_data, metric_label) {
  
  # create grid based on specific data range of the model
  new_data <- expand.grid(
    t_rel = seq(min(original_data$t_rel), max(original_data$t_rel), length.out = 200),
    condition = unique(original_data$condition),
    dyad = original_data$dyad[1] # dummy selection for random effect structure
  )
  
  # predict excluding random effects
  pred <- predict(model, newdata = new_data, se.fit = TRUE, exclude = "s(dyad)")
  
  # return processed frame
  new_data %>%
    mutate(
      fit = pred$fit,
      se = pred$se.fit,
      lower = fit - 1.96 * se,
      upper = fit + 1.96 * se,
      metric = metric_label # adds a label to distinguish plots
    )
}

pred_sr <- get_gam_pred(gam_sr_rel, sync_nc, "SR deviation")
pred_f0 <- get_gam_pred(gam_f0, sync_nc %>% filter(!is.na(F0_rate)), "F0 deviation")
pred_rms <- get_gam_pred(gam_rms, sync_nc %>% filter(!is.na(F0_rate)), "RMS deviation") # assuming same filter as provided

plot_data <- bind_rows(pred_sr, pred_f0, pred_rms)

ggplot(plot_data, aes(x = t_rel, y = fit, color = condition, fill = condition)) +
  # confidence bands
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.3, color = NA) +
  
  # fitted lines
  geom_line(linewidth = 0.5) +
  
  # aesthetics
  scale_color_manual(values = cond_cols) +
  scale_fill_manual(values = cond_cols) +
  
  # facetting: creates separate panels for each metric
  # scales = "free_y" allows each metric to have its own y-axis range
  facet_wrap(~ metric, scales = "free_y", nrow = 1) +
  
  labs(
    x = "Relative time index (scale 0 ~ 1)",
    y = "Predicted value",
    title = "Interlocutor coupling by condition over time",
    # subtitle = "gam estimates excluding random dyadic effects"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "top",
    panel.grid.minor = element_blank(),
    strip.text = element_text(face = "bold", size = 12), # bold facet labels
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank()
  )
ggsave("GAM_fit_group_matrix.png", path = "/Users/moanason/Downloads/Data_ANA/Fig")
```



# iii) frame-wise time-series dataset
### dynamic synchrony: sliding-window correlations (F0 & RMS)
```{r}
# to z-transform by group
z_by_group <- function(x) {
  mu <- mean(x, na.rm = TRUE)
  sd <- sd(x, na.rm = TRUE)
  if (sd == 0 || is.na(sd)) return(rep(NA_real_, length(x)))
  (x - mu) / sd
}

frame_z <- frame_df %>%
  group_by(dyad, condition) %>%
  mutate(
    F0_A_z  = z_by_group(F0_A_sp),
    F0_B_z  = z_by_group(F0_B_sp),
    RMS_A_z = z_by_group(RMS_A_sp),
    RMS_B_z = z_by_group(RMS_B_sp)
  ) %>%
  ungroup()

```

```{r}
WIN_LEN  <- 30   # 30-second windows
STEP_SEC <- 5    # slide every 5 seconds

library(purrr)

compute_window_corr <- function(df, featureA, featureB,
                                win_len = WIN_LEN, step = STEP_SEC) {
  # df must contain time_sec and the two features
  t_min <- min(df$time_sec, na.rm = TRUE)
  t_max <- max(df$time_sec, na.rm = TRUE)
  if (!is.finite(t_min) || !is.finite(t_max) || (t_max - t_min) < win_len) {
    return(tibble())
  }

  centers <- seq(t_min + win_len / 2, t_max - win_len / 2, by = step)

  map_dfr(centers, function(cc) {
    t0 <- cc - win_len / 2
    t1 <- cc + win_len / 2
    sub <- df %>% filter(time_sec >= t0, time_sec < t1)

    if (nrow(sub) < 10) {
      r_val <- NA_real_
    } else {
      r_val <- suppressWarnings(
        cor(sub[[featureA]], sub[[featureB]], use = "pairwise.complete.obs")
      )
    }

    tibble(
      win_center = cc,
      r = r_val
    )
  })
}
```


```{r}
# F0 synchrony
sw_F0 <- frame_z %>%
  group_by(dyad, condition) %>%
  group_modify(~ compute_window_corr(.x, "F0_A_z", "F0_B_z",
                                     win_len = WIN_LEN, step = STEP_SEC)) %>%
  ungroup() %>%
  mutate(feature = "F0")

# RMS synchrony
sw_RMS <- frame_z %>%
  group_by(dyad, condition) %>%
  group_modify(~ compute_window_corr(.x, "RMS_A_z", "RMS_B_z",
                                     win_len = WIN_LEN, step = STEP_SEC)) %>%
  ungroup() %>%
  mutate(feature = "RMS")

sw_all <- bind_rows(sw_F0, sw_RMS)

sw_all %>% head()

```


```{r}
sw_nc <- sw_all %>%
  filter(condition %in% c("NC1", "NC2"))

ggplot(sw_nc, aes(x = win_center / 60, y = r, colour = condition)) +
  geom_smooth(method = "loess", se = TRUE) +
  facet_wrap(~ feature, ncol = 1) +
  scale_color_manual(values = cond_cols) +
  scale_fill_manual(values = cond_cols) +
  labs(
    x = "Time (minutes, window centre)",
    y = "Sliding-window correlation (A vs B)",
    colour = "Condition"
  )
```


```{r f0}
sw_F0_nc <- sw_nc %>% filter(feature == "F0") %>% drop_na(r)

gam_F0_sync <- gam(
  r ~ condition + s(win_center, by = condition, k = 6) + s(dyad, bs = "re"),
  data = sw_F0_nc,
  method = "REML"
)

summary(gam_F0_sync)
plot(gam_F0_sync, pages = 1, shade = TRUE)
```

```{r rms}
sw_RMS_nc <- sw_nc %>% filter(feature == "RMS") %>% drop_na(r)

gam_RMS_sync <- gam(
  r ~ condition + s(win_center, by = condition, k = 6) + s(dyad, bs = "re"),
  data = sw_RMS_nc,
  method = "REML"
)

summary(gam_RMS_sync)
plot(gam_RMS_sync, pages = 1, shade = TRUE)

## overall synchrony (average r) differs between NC1 & NC2
## synchrony increases over time in one condition more than the other

```

```{r fig.height=4, fig.width=8}

get_gam_pred_w <- function(model, original_data, metric_label) {
  
  # create grid based on specific data range of the model
  new_data <- expand.grid(
    win_center = seq(min(original_data$win_center), max(original_data$win_center)),
    condition = unique(original_data$condition),
    dyad = original_data$dyad[1] # dummy selection for random effect structure
  )
  
  # predict excluding random effects
  pred <- predict(model, newdata = new_data, se.fit = TRUE, exclude = "s(dyad)")
  
  # return processed frame
  new_data %>%
    mutate(
      fit = pred$fit,
      se = pred$se.fit,
      lower = fit - 1.96 * se,
      upper = fit + 1.96 * se,
      metric = metric_label # adds a label to distinguish plots
    )
}


pred_f0_w <- get_gam_pred_w(gam_F0_sync, sw_F0_nc, "F0 deviation (windowed)")
pred_rms_w <- get_gam_pred_w(gam_RMS_sync, sw_RMS_nc, "RMS deviation (windowed)") 

plot_data_w <- bind_rows(pred_f0_w, pred_rms_w)

ggplot(plot_data_w, aes(x = win_center, y = fit, color = condition, fill = condition)) +
  # confidence bands
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.3, color = NA) +
  
  geom_line(linewidth = 0.5) +
  
  scale_color_manual(values = cond_cols) +
  scale_fill_manual(values = cond_cols) +
  
  facet_wrap(~ metric, scales = "free_y", nrow = 1) +
  
  labs(
    x = "Conversation progress (windowed)",
    y = "Sliding-window correlation",
    title = "Interlocutor coupling with sliding windows (30-sec)",
    # subtitle = "gam estimates excluding random dyadic effects"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "top",
    panel.grid.minor = element_blank(),
    strip.text = element_text(face = "bold", size = 12), # bold facet labels
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank()
  )
ggsave("GAM_fit_windowed_matrix.png", path = "/Users/moanason/Downloads/Data_ANA/Fig")
```


# iv) CRQA on RMS envelopes per dyad x condition
```{r}
library(crqa)

DS_STEP <- 0.1  #  increase to 100 ms if memory out (i did for 16gb)

rms_ds <- frame_df %>%
  mutate(
    bin = floor(time_sec / DS_STEP)
  ) %>%
  group_by(dyad, condition, bin) %>%
  summarise(
    time_bin = mean(time_sec, na.rm = TRUE),
    RMS_A_bin = mean(RMS_A_sp, na.rm = TRUE),
    RMS_B_bin = mean(RMS_B_sp, na.rm = TRUE),
    .groups = "drop"
  )

z_by_group <- function(x) {
  mu <- mean(x, na.rm = TRUE)
  sd <- sd(x, na.rm = TRUE)
  if (sd == 0 || is.na(sd)) return(rep(NA_real_, length(x)))
  (x - mu) / sd
}

rms_ds_z <- rms_ds %>%
  group_by(dyad, condition) %>%
  mutate(
    RMS_A_z = z_by_group(RMS_A_bin),
    RMS_B_z = z_by_group(RMS_B_bin)
  ) %>%
  ungroup()
```


```{r}
rms_ts_ds <- rms_ds_z %>%
  group_by(dyad, condition) %>%
  summarise(
    RMS_A_ts = list(na.omit(RMS_A_z)),
    RMS_B_ts = list(na.omit(RMS_B_z)),
    .groups = "drop"
  )

rms_ts_ds %>% head()
```


```{r}
compute_crqa_metrics <- function(ts1, ts2,
                                 delay = 1,
                                 embed = 2, # parameters (delay, embed, radius, etc.) can be tuned; here’s a starting point for continuous z-scored RMS at 20 ms -> 100ms resolution
                                 radius = 0.5,
                                 mindiagline = 2,
                                 minvertline = 2,
                                 tw = 0) {

  ts1 <- as.numeric(ts1)
  ts2 <- as.numeric(ts2)

  # crqa expects no NAs
  mask <- is.finite(ts1) & is.finite(ts2)
  ts1 <- ts1[mask]
  ts2 <- ts2[mask]

  # if too short, return NAs
  if (length(ts1) < 50 || length(ts2) < 50) {
    return(tibble(
      RR = NA_real_, DET = NA_real_, L = NA_real_, Lmax = NA_real_,
      ENTR = NA_real_, LAM = NA_real_, TT = NA_real_
    ))
  }

  res <- crqa(
    ts1, ts2,
    delay       = delay,
    embed       = embed,
    rescale     = 0,      # already z-scaled
    radius      = radius,
    normalize   = 0,
    mindiagline = mindiagline,
    minvertline = minvertline,
    tw          = tw,
    whiteline   = TRUE,
    recpt       = FALSE,
    side        = "both",
    method      = "crqa"
  )

  tibble(
    RR    = res$RR,
    DET   = res$DET,
    L     = res$L,
    Lmax  = res$Lmax,
    ENTR  = res$ENTR,
    LAM   = res$LAM,
    TT    = res$TT
  )
}

```


```{r}
library(purrr)

crqa_df <- rms_ts_ds %>%
   mutate(
     crqa = map2(RMS_A_ts, RMS_B_ts, ~ compute_crqa_metrics(.x, .y))
   ) %>%
   unnest(crqa)

crqa_df
```


```{r}
crqa_nc <- crqa_df %>%
  filter(condition %in% c("NC1", "NC2"))

m_DET <- lmer(DET ~ condition + (1 | dyad), data = crqa_nc)
summary(m_DET)
anova(m_DET)

m_RR <- lmer(RR ~ condition + (1 | dyad), data = crqa_nc)
summary(m_RR)
anova(m_RR)

m_Lmax <- lmer(L ~ condition + (1 | dyad), data = crqa_nc)
summary(m_Lmax)
anova(m_Lmax)
```

```{r fig.width=8, fig.height=5}
crqa_long <- crqa_nc %>%
  dplyr::select(condition, DET, RR, L) %>%
  pivot_longer(
    cols = c(DET, RR, L),
    names_to = "metric",
    values_to = "value"
  ) %>%
  mutate(
    condition = factor(condition),
    metric = factor(
      metric,
      levels = c("DET", "RR", "L"),
      labels = c("DET (Determinism)", "RR (Recurrence rate)", "Lmax (L)")
    )
  )

ggplot(crqa_long, aes(x = condition, y = value, colour = condition)) +
  geom_boxplot(outlier.alpha = 0.4) +
  geom_point(alpha = 0.5) +
  scale_color_manual(values = cond_cols) +
  scale_fill_manual(values = cond_cols) +
  facet_wrap(~ metric, ncol = 3, scales = "free_y") +
  labs(x = "Condition", y = "CRQA metric value", colour = "Condition", fill = "Condition") +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )
ggsave("crqa_rms_coupling.png", path = "/Users/moanason/Downloads/Data_ANA/Fig")

```

as NC2 shows higher DET / RR / Lmax than NC1, thus after the synchrony task, the dyads’ RMS envelopes exhibit more structured and stable coupling in their dynamics, as indicated by higher CRQA determinism and recurrence rate.



--------------------------------------------------------------------------------
# v) sync level x turn-taking events

```{r}
library(dplyr)
library(mclust)

pairs <- sync_nc %>%
  mutate(row_id = dplyr::row_number())

sync_df <- pairs %>%
  dplyr::select(row_id, dyad, condition, M_rate, F0_rate, RMS_rate) %>%
  dplyr::filter(is.finite(M_rate),
         is.finite(F0_rate),
         is.finite(RMS_rate))

sync_df <- sync_df %>%
  mutate(
    z_rate = as.numeric(scale(M_rate)),   # z-score of M_rate
    z_F0   = as.numeric(scale(F0_rate)),     # z-score of M_F0
    z_RMS  = as.numeric(scale(RMS_rate))     # z-score of M_RMS
  )

w_rate <- 1/3
w_F0   <- 1/3
w_RMS  <- 1/3

sync_df <- sync_df %>%
  mutate(
    C = w_rate * z_rate +
        w_F0   * z_F0   +
        w_RMS  * z_RMS
  )


# build matrix
X <- sync_df %>%
  dplyr::select(z_rate, z_F0, z_RMS) %>%
  as.matrix()

dim(X)
head(X)
```

```{r}
# fit a dummy three level Gaussian, attempt only, not used at the end
set.seed(123)  # for reproducibility

gmm3 <- Mclust(X, G = 3)  # force G = 3 components

print(gmm3$G)              # should be 3
print(gmm3$modelName)      # e.g. "VVV" etc.
table(gmm3$classification) # cluster sizes

sync_df$cluster <- gmm3$classification

cluster_means <- sync_df %>%
  group_by(cluster) %>%
  summarise(
    mean_C = mean(C, na.rm = TRUE),
    n      = dplyr::n(),
    .groups = "drop"
  ) %>%
  arrange(mean_C)

cluster_means

labels_by_order <- c("high", "medium", "low")

cluster_map <- cluster_means %>%
  mutate(sync_level = labels_by_order) %>%
  dplyr::select(cluster, sync_level)

sync_df <- sync_df %>%
  left_join(cluster_map, by = "cluster") %>%
  mutate(
    sync_level = factor(sync_level,
                        levels = c("low", "medium", "high"))
  )

table(sync_df$sync_level)

sr_nc <- pairs %>%
  left_join(
    sync_df %>%
      dplyr::select(row_id, cluster, sync_level),
    by = "row_id"
  )
```



## sync ~ event (core statistics!)
```{r}
event_df <- read_csv("/Users/moanason/Downloads/Data_ANA/descriptive_processed_event_data.csv")

event_df <- event_df %>%
  mutate(
    dyad      = factor(i),
    condition = factor(
      c,
      levels = c(0, 1, 2),
      labels = c("NC1", "NC2", "NS")
    ),
    speaker_factor = case_when(
      speaker == 0 ~ "A",
      speaker == 1 ~ "B",
      TRUE         ~ NA_character_   # for Gap/Silence/Overlap
    ),
    speaker_factor = factor(speaker_factor, levels = c("A", "B"))
  )

sr_nc_macro <- sync_nc %>%
  dplyr::mutate(
    macro_start = start_time,
    macro_end   = end_next
  )

event_df2 <- event_df %>%
  dplyr::mutate(
    event_start = time_sec,
    event_end   = time_sec + duration,
    is_gap      = grepl("Gap",        event, ignore.case = TRUE),
    is_overlap  = grepl("Overlap",    event, ignore.case = TRUE),
    is_bc       = grepl("Backchannel",event, ignore.case = TRUE)
  ) %>%
  dplyr::select(
    i, c, dyad, condition,
    event, duration,
    event_start, event_end,
    is_gap, is_overlap, is_bc
  )

macro_event_long <- sr_nc_macro %>%
  dplyr::select(
    i, c, dyad, condition,
    pair_idx,               # pair identifier for the macro-turn pair
    macro_start, macro_end
    ) %>%
  inner_join(
    event_df2,
    by = c("i", "c", "dyad", "condition")
  ) %>%
  # Keep only events that intersect [macro_start, macro_end)
  dplyr::filter(
    event_start < macro_end,
    event_end   > macro_start
  ) %>%
  dplyr::mutate(
    overlap_start = pmax(macro_start, event_start),
    overlap_end   = pmin(macro_end,   event_end),
    overlap_dur   = pmax(0, overlap_end - overlap_start)
  )

macro_event_summary <- macro_event_long %>%
  group_by(i, c, dyad, condition, pair_idx) %>%
  summarise(
    has_gap      = any(is_gap     & overlap_dur > 0),
    has_overlap  = any(is_overlap & overlap_dur > 0),
    macro_gap_dur = sum(overlap_dur[is_gap],     na.rm = TRUE),
    macro_ovl_dur = sum(overlap_dur[is_overlap], na.rm = TRUE),
    macro_bc     = sum(overlap_dur[is_bc], na.rm = TRUE),             # total BC time
    macro_bc_n   = sum(is_bc & overlap_dur > 0, na.rm = TRUE),        # number of BC events
    .groups = "drop"
  ) %>%
  dplyr::mutate(
    macro_trE_dur = macro_gap_dur + macro_ovl_dur,
    macro_events = case_when(
      has_gap & has_overlap ~ "Gap+Overlap",
      has_gap               ~ "Gap",
      has_overlap           ~ "Overlap",
      TRUE                  ~ "None"
    ),
    macro_events = factor(
      macro_events,
      levels = c("None", "Gap", "Overlap", "Gap+Overlap")
    )
  ) %>%
  dplyr::select(
    i, c, dyad, condition, pair_idx,
    macro_events,
    macro_gap_dur, macro_ovl_dur, macro_trE_dur,
    macro_bc, macro_bc_n
  )

sr_nc <- sr_nc_macro %>%
  left_join(macro_event_summary,
            by = c("i", "c", "dyad", "condition", "pair_idx")) %>%
  mutate(
    macro_pair_dur = macro_end - macro_start,
    macro_gap_dur = replace_na(macro_gap_dur, 0),
    macro_ovl_dur = replace_na(macro_ovl_dur, 0),
    macro_trE_dur = replace_na(macro_trE_dur, 0),
    macro_bc      = replace_na(macro_bc, 0),
    macro_bc_n    = replace_na(macro_bc_n, 0L),

    macro_trE_prop = if_else(macro_pair_dur > 0,
                             macro_trE_dur / macro_pair_dur,
                             NA_real_),
    macro_bc_prop  = if_else(macro_pair_dur > 0,
                             macro_bc / macro_pair_dur,
                             NA_real_),
    macro_events = forcats::fct_explicit_na(macro_events, na_level = "None")
  )


table(sr_nc$macro_events, sr_nc$condition)
summary(sr_nc$macro_bc)
summary(sr_nc$macro_bc_n)

```


### delta+events

```{r} 
# dummy try with sr
sr_nc <- sr_nc %>%
  mutate(
    macro_events = factor(macro_events,
                          levels = c("None", "Gap", "Overlap", "Gap+Overlap")),
    condition    = factor(condition),
    dyad         = factor(dyad)
  )
```


```{r}
library(dplyr)

sr_nc_cont <- sr_nc %>%
  # keep rows that actually have synchrony values
  filter(!is.na(M_rate), !is.na(F0_rate), !is.na(RMS_rate)) %>%
  mutate(
    # z-scores (across all dyads and conditions)
    z_rate = as.numeric(scale(M_rate)),
    z_F0   = as.numeric(scale(F0_rate)),
    z_RMS  = as.numeric(scale(RMS_rate)),

    # composite mismatch index: mean of the three z-scores
    mismatch_index = (z_rate + z_F0 + z_RMS) / 3,

    # opt: convert to "synchrony" (higher = more synchrony)
    sync_index = -mismatch_index,

    # make sure factors are coded nicely
    condition = factor(condition, levels = c("NC1", "NC2")),
    # macro_events = factor(
    #   macro_events,
    #   levels = c("none", "gap_only", "ovl_only", "gap+ovl")
    # ),
    dyad = factor(dyad)
  )
```

## we fit a full-crossed contrast coding to the LMM (VITAL)
```{r}
sr_nc_cont$condition <- factor(sr_nc_cont$condition, levels = c("NC1", "NC2"))
sr_nc_cont$macro_events <- factor(sr_nc_cont$macro_events, levels = c("None", "Gap", "Overlap", "Gap+Overlap"))
contrasts(sr_nc_cont$condition) <- contr.sum(2) 
contrasts(sr_nc_cont$macro_events) <- contr.sum(length(unique(sr_nc_cont$macro_events)))
colnames(contrasts(sr_nc_cont$condition)) <- levels(sr_nc_cont$condition)[-1]
colnames(contrasts(sr_nc_cont$macro_events)) <- levels(sr_nc_cont$macro_events)[-1]
m_sync <- lmer(
  sync_index ~ condition * macro_events * macro_trE_dur +
    macro_bc * macro_bc_n + t_rel + pair_sx +
    (1 + condition | dyad),
  data = sr_nc_cont
)

summary(m_sync)
anova(m_sync)
```


```{r fig.height=4, fig.width=6} 
library(emmeans)
emm_sync <- lmer(
  sync_index ~ condition * macro_events +
    macro_bc * macro_bc_n + t_rel + pair_sx +
    (1 + condition | dyad),
  data = sr_nc_cont
)
emm_sync <- emmeans(emm_sync, ~ macro_events | condition) # simple plot

plot(emm_sync)   # quick diagnostic plot


cond_cols <- c(
  "NC1" = "#87CEEB", 
  "NC2" = "#7570b3",  
  "NS"  = "#FFFFAA"  
)

# Publication-style plot
emm_df <- as.data.frame(emm_sync)

ggplot(emm_df, aes(x = macro_events, y = emmean,
                   colour = condition, group = condition)) +
  geom_point(position = position_dodge(width = 0.4), size = 2) +
  geom_errorbar(
    aes(ymin = emmean - SE, ymax = emmean + SE),
    width = 0.15,
    position = position_dodge(width = 0.4)
  ) +
  scale_colour_manual(values = c("NC1" = "#87CEEB", "NC2" = "#7570b3")) +
  labs(
    x = "Transitional Events",
    y = "Synchrony (higher = more synchronous)",
    colour = "Condition",
    title = "Effect of Gap/Overlap on Continuous Synchrony"
  ) +
  theme_minimal() +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank()
  )
ggsave("events_on_synchrony.png", path = "/Users/moanason/Downloads/Data_ANA/Fig")
```

```{r fig.width=6, fig.height=4}
sync_bins <- sr_nc_cont %>% # plot the dynamic change of the matrix, same as before a singular factor (e.g., SR)
  mutate(
    bin = cut(
      t_rel,
      breaks = seq(0, 1, length.out = 21),
      include.lowest = TRUE,
      labels = FALSE
    )
  ) %>%
  group_by(condition, bin) %>%
  summarise(
    sync_mean = mean(sync_index, na.rm = TRUE),
    sync_se   = sd(sync_index, na.rm = TRUE) / sqrt(n()),
    .groups = "drop"
  ) %>%
  mutate(
    bin_center = (bin - 0.5) / 20   # 0.1, 0.3, 0.5, 0.7, 0.9
  )

ggplot(sync_bins,
       aes(x = bin_center, y = sync_mean, colour = condition, group = condition)) +
  geom_line(linewidth = 0.5, alpha = 0.7) +
  geom_point(alpha = 0.7) +
  scale_color_manual(values = cond_cols) +
  scale_fill_manual(values = cond_cols) +
  # geom_smooth(stat = "smooth",
  # position = "identity", se = F, linewidth = 0.7) +
  geom_errorbar(aes(ymin = sync_mean - sync_se, ymax = sync_mean + sync_se), width = 0.01, alpha = 0.2) +
  labs(
    x = "Conversation progress",
    y = "Mean sync mismatch: z[SR, F0, RMS]",
    colour = "Condition"
  ) +
  theme_minimal() +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank()
  )
ggsave("mean_sync_dev.png", path = "/Users/moanason/Downloads/Data_ANA/Fig")
```


```{r fig.width=12, fig.height=8}
library(dplyr)
library(tidyr)
library(ggplot2)

long_bins <- sr_nc_cont %>%
  dplyr::mutate(
    sync_rate = -z_rate,
    sync_F0   = -z_F0,
    sync_RMS  = -z_RMS
  ) %>%
  dplyr::select(condition, t_rel, sync_index, sync_rate, sync_F0, sync_RMS) %>%
  pivot_longer(
    cols = c(sync_index, sync_rate, sync_F0, sync_RMS),
    names_to = "metric",
    values_to = "sync_value"
  ) %>%
  mutate(
    metric = factor(metric,
      levels = c("sync_rate","sync_F0","sync_RMS","sync_index"),
      labels = c("Speech rate","F0","RMS","C[SR, F0, RMS]")
    ),
    bin = cut(t_rel, breaks = seq(0,1,length.out=21), include.lowest=TRUE, labels=FALSE)
  ) %>%
  group_by(condition, metric, bin) %>%
  summarise(
    sync_mean = mean(sync_value, na.rm = TRUE),
    sync_se   = sd(sync_value, na.rm = TRUE) / sqrt(sum(!is.na(sync_value))),
    .groups = "drop"
  ) %>%
  mutate(bin_center = (bin - 0.5) / 20)

ggplot(long_bins, aes(x = bin_center, y = sync_mean, colour = condition, group = condition)) +
  geom_line(linewidth = 0.5, alpha = 0.7) +
  geom_point(alpha = 0.7) +
  geom_errorbar(aes(ymin = sync_mean - sync_se, ymax = sync_mean + sync_se),
                width = 0.01, alpha = 0.2) +
  scale_color_manual(values = cond_cols) +
  facet_wrap(~ metric, ncol = 2, scales = "free_y") +
  labs(x = "Conversation progress (scale 0 ~ 1)", y = "Synchrony level (higher = more synchronous)", colour = "Condition") +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank()
  )
ggsave("mean_sync_dev.png", path = "/Users/moanason/Downloads/Data_ANA/Fig")
```



```{r}
library(dplyr)
library(tidyr)
library(purrr)
library(stringr)

library(broom)
library(broom.mixed)
library(mgcv)

library(performance)
library(gt)
library(kableExtra)

```


```{r}
extract_lmm <- function(mod, model_name, analysis, outcome = NA_character_, level = 0.95) {

  fe <- broom.mixed::tidy(
    mod,
    effects = "fixed",
    conf.int = TRUE,
    conf.level = level,
    conf.method = "Wald"   # fast; "profile" is slower but sometimes preferred
  ) %>%
    mutate(
      model      = model_name,
      analysis   = analysis,
      outcome    = outcome,
      model_type = "LMM",
      term_type  = "parametric",
      stat_name  = "t"
    )

  fit <- tibble(
    model      = model_name,
    analysis   = analysis,
    outcome    = outcome,
    model_type = "LMM",
    n_obs      = nobs(mod),
    AIC        = AIC(mod),
    BIC        = BIC(mod),
    logLik     = as.numeric(logLik(mod))
  )

  list(term_table = fe, fit_table = fit)
}


# extract_gam <- function(mod, model_name, analysis, outcome = NA_character_) {
# 
#   s <- summary(mod)

extract_gam <- function(mod, model_name, analysis, outcome = NA_character_, level = 0.95) {

  s <- summary(mod)
  alpha <- 1 - level
  crit  <- qnorm(1 - alpha/2)  # ~1.96 for 95%

  # parametric terms (with CI)
  ptab <- as.data.frame(s$p.table) %>%
    tibble::rownames_to_column("term") %>%
    rename(
      estimate  = Estimate,
      std.error = `Std. Error`,
      statistic = `t value`,
      p.value   = `Pr(>|t|)`
    ) %>% 
    mutate(
      conf.low  = estimate - crit * std.error,
      conf.high = estimate + crit * std.error,
      model      = model_name,
      analysis   = analysis,
      outcome    = outcome,
      model_type = "GAM",
      term_type  = "parametric",
      stat_name  = "t"
    )

  # smooth terms
  stab <- as.data.frame(s$s.table) %>%
    tibble::rownames_to_column("term") %>%
    rename(
      edf = edf,
      ref.df = Ref.df,
      statistic = F,
      p.value = `p-value`
    ) %>%
    mutate(
      estimate   = NA_real_,
      std.error  = NA_real_,
      conf.low   = NA_real_,
      conf.high  = NA_real_,
      model      = model_name,
      analysis   = analysis,
      outcome    = outcome,
      model_type = "GAM",
      term_type  = "smooth",
      stat_name  = "F"
    )

  fit <- tibble(
    model      = model_name,
    analysis   = analysis,
    outcome    = outcome,
    model_type = "GAM",
    n_obs      = nobs(mod),
    AIC        = AIC(mod),
    BIC        = BIC(mod),
    dev_expl   = s$dev.expl,
    r_sq_adj   = s$r.sq
  )

  list(term_table = bind_rows(ptab, stab), fit_table = fit)
}


extract_ttest <- function(tt, model_name, analysis, outcome, level = 0.95) {
  broom::tidy(tt, conf.int = TRUE, conf.level = level) %>%
    transmute(
      model      = model_name,
      analysis   = analysis,
      outcome    = outcome,
      model_type = "t-test",
      term_type  = "parametric",
      term       = "NC2 - NC1",
      estimate   = estimate,
      std.error  = NA_real_,
      statistic  = statistic,
      p.value    = p.value,
      conf.low   = conf.low,
      conf.high  = conf.high,
      stat_name  = "t"
    )
}


```



```{r}
models <- list(
  # --- Global LMMs ---
  list(obj = m_sr_mean,   name = "LMM_Global_SR",  analysis = "Global synchrony (LMM)", outcome = "M_rate / devs"),
  list(obj = m_f0,   name = "LMM_Global_F0",  analysis = "Global synchrony (LMM)", outcome = "F0 / devs"),
  list(obj = m_rms,   name = "LMM_Global_RMS",  analysis = "Global synchrony (LMM)", outcome = "RMS / devs"),
  list(obj = m_F0_sim,    name = "LMM_H1H2_F0",    analysis = "Global H1/H2 (LMM)", outcome = "F0 / sims"),
  list(obj = m_RMS_sim,    name = "LMM_H1H2_RMS",    analysis = "Global H1/H2 (LMM)", outcome = "RMS / sims"),
  list(obj = m_F0_conv,    name = "LMM_H1H2_F0",    analysis = "Global H1/H2 (LMM)", outcome = "F0 / conv"),
  list(obj = m_RMS_conv,    name = "LMM_H1H2_RMS",    analysis = "Global H1/H2 (LMM)", outcome = "RMS / conv"),

  # --- GAMMs (sr, f0, rms) ---
  list(obj = gam_sr_rel,  name = "GAM_SR",      analysis = "Time-resolved synchrony (GAM)", outcome = "M_rate"),
  list(obj = gam_f0,      name = "GAM_F0",      analysis = "Time-resolved synchrony (GAM)", outcome = "F0_dev"),
  list(obj = gam_rms,     name = "GAM_RMS",     analysis = "Time-resolved synchrony (GAM)", outcome = "RMS_dev"),

  # --- Sliding-window GAMs (examples) ---
  list(obj = gam_F0_sync,   name = "GAM_SW_F0",   analysis = "Sliding-window entrainment (GAM)", outcome = "win_cor_F0"),
  list(obj = gam_RMS_sync,  name = "GAM_SW_RMS",  analysis = "Sliding-window entrainment (GAM)", outcome = "win_cor_RMS"),

  # CRQA
  list(obj = m_DET,    name = "LMM_CRQA_DET",    analysis = "CRQA analysis on RMS (LMM)", outcome = "DET"),
  list(obj = m_RR,     name = "LMM_CRQA_RR",    analysis = "CRQA analysis on RMS (LMM)", outcome = "RR"),
  list(obj = m_Lmax,   name = "LMM_CRQA_Lmax",    analysis = "CRQA analysis on RMS (LMM)", outcome = "Lmax"),
  
  # --- Sync Index LMM ---
  list(obj = m_sync, name = "LMM_SYNC", analysis = "Composite synchrony index (LMM)", outcome = "sync_index")
)
```


```{r}
all_terms <- list()
all_fit   <- list()

for (m in models) {
  if (inherits(m$obj, "lmerMod")) {
    out <- extract_lmm(m$obj, m$name, m$analysis, m$outcome)
  } else if (inherits(m$obj, "gam")) {
    out <- extract_gam(m$obj, m$name, m$analysis, m$outcome)
  } else {
    stop("Unknown model class for: ", m$name)
  }
  all_terms[[m$name]] <- out$term_table
  all_fit[[m$name]]   <- out$fit_table
}

terms_tbl <- bind_rows(all_terms)
fit_tbl   <- bind_rows(all_fit)
```

```{r}
key_terms <- c(
  "Intercept",
  "conditionNC2",
  "s\\(t_rel", "s\\(t_rel_idx", "s\\(pair_idx", "s\\(t_cum",   # smooth time terms
  "macro_events", "macro_bc", "macro_bc_n", "macro_trE_dur"    # your event predictors
)

report_tbl <- terms_tbl %>%
  mutate(term = as.character(term)) %>%
  filter(
    str_detect(term, str_c(key_terms, collapse = "|"))
  ) %>%
  mutate(
    estimate  = round(estimate, 4),
    std.error = round(std.error, 4),
    conf.low  = round(conf.low, 3),
    conf.high = round(conf.high, 3),
    CI = ifelse(!is.na(conf.low),
                   paste0("[", conf.low, ", ", conf.high, "]"),
                   NA_character_),
    statistic = round(statistic, 3),
    p.value   = signif(p.value, 3)
  ) %>%
  dplyr::select(analysis, model, outcome, model_type, term_type, term,
         estimate, std.error, CI, -conf.low, -conf.high, stat_name, statistic, p.value)


# if (!("conf.low" %in% names(report_tbl))) report_tbl$conf.low  <- NA_real_
# if (!("conf.high" %in% names(report_tbl))) report_tbl$conf.high <- NA_real_

# report_tbl <- report_tbl %>%
#   mutate(
#     conf.low  = round(conf.low, 3),
#     conf.high = round(conf.high, 3),
#     CI = ifelse(!is.na(conf.low),
#                    paste0("[", conf.low, ", ", conf.high, "]"),
#                    NA_character_)
#   ) %>%
#   dplyr::select(-conf.low, -conf.high)


report_tbl <- report_tbl %>%
  mutate(
    signif = case_when(
      is.na(p.value)        ~ NA_character_,
      p.value < 0.001       ~ "***",
      p.value < 0.01        ~ "**",
      p.value < 0.05        ~ "*",
      p.value < 0.1         ~ ".",
      TRUE                  ~ ""
    )
  )

report_tbl %>%
  dplyr::select(analysis, model, outcome, model_type, term_type, term,
         estimate, std.error, CI, statistic, p.value, stat_name)

```

```{r}
gt_table <- report_tbl %>%
  gt(groupname_col = "analysis") %>%
  tab_header(title = "Synchrony modelling summary table") %>%
  cols_label(
    model = "Model",
    outcome = "Outcome",
    model_type = "Type",
    term_type = "Term class",
    term = "Term",
    estimate = "Est.",
    std.error = "SE",
    CI = "CI",
    stat_name = "",
    statistic = "Stat",
    p.value = "p",
  ) %>%
  fmt_missing(everything(), missing_text = "") %>%
  # gt::cols_hide(columns = c(conf.low, conf.high)) %>%
  tab_options(table.width = pct(100))

gt_table
```

```{r}
out_path <- "/Users/moanason/Downloads/Data_ANA/synchrony_model_table.tex"
gtsave(gt_table, filename = out_path)
```

```{r}
library(dplyr)
library(knitr)
library(kableExtra)

tab_tex <- report_tbl 

tex_code <- kable(
  tab_tex,
  format = "latex",
  booktabs = TRUE,
  longtable = TRUE,
  caption = "Synchrony modelling summary table"
) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))

out_path <- "/Users/moanason/Downloads/Data_ANA/synchrony_model_table.tex"
writeLines(tex_code, out_path)

out_path

```


```{r}
library(dplyr)
library(knitr)
library(kableExtra)

# tab_tex must contain a column called `analysis`
tab_tex2 <- tab_tex %>%
  arrange(analysis)   # important: grouping assumes contiguous blocks

# 1) base table
tex_kbl <- tab_tex2 %>%
  kable(
    format = "latex",
    booktabs = TRUE,
    longtable = TRUE,
    caption = "Synchrony modelling summary table",
    escape = FALSE
  ) %>%
  kable_styling(latex_options = c("repeat_header"))  # NOTE: hold_position doesn't apply to longtable

# 2) add grouped row blocks
grp_sizes  <- tab_tex2 %>% dplyr::count(analysis, name = "n") %>% pull(n)
grp_labels <- tab_tex2 %>% distinct(analysis) %>% pull(analysis)

for (g in seq_along(grp_sizes)) {
  tex_kbl <- tex_kbl %>%
    pack_rows(grp_labels[g], start_row = sum(grp_sizes[seq_len(g-1)]) + 1,
                           end_row   = sum(grp_sizes[seq_len(g)]),
              bold = TRUE, italic = FALSE)
}

# 3) save
out_path <- "/Users/moanason/Downloads/Data_ANA/synchrony_model_table.tex"
writeLines(tex_kbl, out_path)

out_path

```



















